### 2020-01-10 README.Rmd
README: add circle ci badge, upd .bib, upd images

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/mlr-org/mlr3spatiotempcv.svg?branch=master)](https://travis-ci.org/mlr-org/mlr3spatiotempcv)
[![cran checks](https://cranchecks.info/badges/worst/mlr3spatiotempcv)](https://cran.r-project.org/web/checks/check_results_mlr3spatiotempcv.html)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotempcv/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotempcv?branch=master)
<!-- badges: end -->

@@

| Literature Name | R Package | Reference | mlr3spatiotempcv Name |
| --------------- | --------- | --------- | ----------------------- |
| Spatial CV  | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `ResampleSpCVCoords`  |
| Spatial Blocking | [blockCV](https://github.com/rvalavi/blockCV) | Valavi 2019 | `ResampleSpCVBlock`   |
| Environmental Blocking | [blockCV](https://github.com/rvalavi/blockCV) | Valavi 2019 | `ResampleSpCVEnv`   |
| Spatial Buffering | [blockCV](https://github.com/rvalavi/blockCV) | Valavi 2019 | `ResampleSpCVBuffer` |

>>>>

<!-- badges: start -->
[![Build Status](https://img.shields.io/travis/mlr-org/mlr3spatiotempcv/master?label=Linux&logo=travis&style=flat-square)](https://travis-ci.org/mlr-org/mlr3spatiotempcv)
[![CircleCI build status](https://circleci.com/gh/mlr-org/mlr3spatiotempcv.svg?style=svg)](https://circleci.com/gh/mlr-org/mlr3spatiotempcv)
[![CRAN Status Badge](https://www.r-pkg.org/badges/version-ago/mlr3spatiotempcv)](https://cran.r-project.org/package=mlr3spatiotempcv)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotempcv/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotempcv?branch=master)
<!-- badges: end -->

@@

| Literature Name        | R Package                                                 | Reference     | mlr3spatiotempcv Class Name | mlr3 sugar            |
| ---------------        | ---------                                                 | ---------     | ---------------------       | --------------------- |
| Spatial Buffering      | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResampleSpCVBuffer`        | `rsmp("spcv-buffer")` |
| Spatial Blocking       | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResampleSpCVBlock`         | `rsmp("spcv-block")`  |
| Spatial CV             | [sperrorest](https://github.com/giscience-fsu/sperrorest) | Brenning 2012 | `ResampleSpCVCoords`        | `rsmp("spcv-coords")` |
| Environmental Blocking | [blockCV](https://github.com/rvalavi/blockCV)             | Valavi 2019   | `ResampleSpCVEnv`           | `rsmp("spcv-env")`    |
